The Impact of Accretion Disk Winds on the Optical Spectra of Cataclysmic Variables

### 2014-12-22 draft.tex
added pdf version to repo

Figure~\ref{wind} shows the physical and ionization structure 
of the benchmark disk wind model. There is an obvious drop-off in density
and temperature with distance away from the disk, so any line
formation process that scales as $\rho^2$ - i.e. recombination and
collisionally excited emission - should be expected to operate
primarily in the dense base of the outflow. Moreover, a comparison of
the rotational and poloidal velocity fields shows that rotation
dominates in the near-disk regime, while outflow dominates further out
in the wind.

@@

\renewcommand{\labelitemi}{$\bullet$}
\begin{itemize}
	\item fill in the Balmer absorption edge in the spectrum of
          the accretion, thus accounting for absence of this edge in
          observed CV spectra \citep{KLWB98};
	\item produce the commonly observed single-peaked optical line
          profiles \citep{MC96}
\end{itemize}
\smallskip

>>>>

Figure~\ref{wind} shows the physical and ionization structure 
of the benchmark disk wind model. The ionization parameter shown in the bottom
right panel is given by

\begin{eqnarray}
U&=&\frac{Q_H}{4\pi R^2 n_{H} c}\\ 
  &=& \frac{4\pi}{n_H c}\int_{13.6{\rm{eV}}}^{\infty}\frac{{J_{\nu}d\nu}}{h\nu}
\end{eqnarray}

where $\rm{Q_H}$ is the number of hydrogen-ionizing photons emitted by
the illuminating source per second, $R$ is the distance to the source,
$\rm{n_H}$ is the local hydrogen number density and $c$ is the speed of
light. $J_\nu$ is the MC estimator for the mean intensity in the cell. 
The ionization parameter is a useful measure
of the ionization state of a plasma, as it evaluates the ratio 
of the integrated ionizing radiation field and the local Hydrogen density.

There is an obvious drop-off in density
and temperature with distance away from the disk, so any line
formation process that scales as $\rho^2$ - i.e. recombination and
collisionally excited emission - should be expected to operate
primarily in the dense base of the outflow. Moreover, a comparison of
the rotational and poloidal velocity fields shows that rotation
dominates in the near-disk regime, while outflow dominates further out
in the wind.

@@

\renewcommand{\labelitemi}{$\bullet$}
\begin{itemize}
	\item fill in the Balmer absorption edge in the spectrum of
          the accretion, thus accounting for the absence of a strong edge in
          observed CV spectra \citep{KLWB98};
	\item produce the commonly observed single-peaked optical line
          profiles (MC96)
\end{itemize}
\smallskip
